---
title: "Tanzania_Tourism_Classisfication_Challenge"
author: "Ridhiwan Mseya"
date: "6/2/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install packages if they dont exist

```{r, warning=FALSE}
if(!require(tidyverse)) install.packages("tidyverse")
if(!require(readr)) install.packages("readr")

```

## load libraries and data files

  Get all the files and some of the libraries that we need to analyze data.
```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(readr)

VariableDefs <- read_csv("VariableDefinitions.csv")
test_data <- read_csv("Test.csv")
Submissionsamp <-read_csv("SampleSubmission.csv")
train_data <- read_csv("Train.csv")
```

## Check the data and remove any missing values


```{r , warning=FALSE, message=FALSE}
head(tibble(VariableDefs)) # contains definitions of each variable/column in our data
head(tibble(train_data)) # The training data for our model which will be split into test and train
head(tibble(test_data)) # The validation data for our model
head(tibble(Submissionsamp)) # The probability of each tour_id to be at a given category.

mean(is.na(train_data)) # if not zero then we have some missing values
mean(is.na(test_data)) # if not zero then we have some missing values

train_data_comp <- na.exclude(train_data) # exclude rows with any NA values
test_data_comp <- na.exclude(test_data) # exclude rows with any NA values

mean(is.na(train_data_comp)) # if not zero then we have some missing values
mean(is.na(test_data_comp)) # if not zero then we have some missing values

```
  The last datasets are complete with no missing values, we can now move on to visualizing our data.
  
```{r , message=FALSE, warning=FALSE}
#plot a graph to visualize the cost category distribution

#factor(train_data_comp$cost_category)
train_data_comp %>% summarise(cost_category) %>% ggplot(aes(cost_category)) + geom_histogram(stat = "count")

```

  If picked at random the probability of a tourist to be a in given cost category would follow this descending order:
  
  Normal Cost -> Higher Cost -> High Cost -> Low Cost -> Lower Cost -> Highest Cost
  
  To predict the cost of a single tourist correctly then we will have to investigate the variables and how they affect the cost category. Let us plot a correlation plot to get an initial picture.
  
```{r , warning=FALSE, message=FALSE}
library(corrplot)

# Make all the data numeric for correlation plots
factorized <- lapply(train_data_comp,as.factor)
corr_data <- lapply(factorized,as.numeric)
train_data_corr <- as.data.frame(corr_data)

# plot the graph
tdr <- cor(train_data_corr)
corrplot(tdr,type = "upper", order = "hclust")
```

  The plot shows us that there is positive correlation between packages that tourists buy and that those packages have a negative correlation with the cost category.The higher the cost the more packages have been used. These variables will heavily affect our prediction models when tweaked.
  

## Machine Learning models

  The criteria in this project will be using the method of log loss.
  

