---
title: "Tanzania_Tourism_Classisfication_Challenge"
author: "Ridhiwan Mseya"
date: "6/2/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install packages if they dont exist

```{r, warning=FALSE}
if(!require(tidyverse)) install.packages("tidyverse")
if(!require(readr)) install.packages("readr")
if(!require(corrplot)) install.packages("corrplot")
if(!require(caret)) install.packages("caret")
if(!require(VGAM)) install.packages("VGAM")
if(!require(RANN)) install.packages("RANN")
if(!require(RWeka)) install.packages("RWeka")
if(!require(obliqueRF)) install.packages("obliqueRF")


```

## load libraries and data files

  Get all the files and some of the libraries that we need to analyze data.
```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(readr)

VariableDefs <- read_csv("VariableDefinitions.csv")
test_data <- read_csv("Test.csv")
Submissionsamp <-read_csv("SampleSubmission.csv")
train_data <- read_csv("Train.csv")
```

## Check the data and remove any missing values


```{r , warning=FALSE, message=FALSE}
head(tibble(VariableDefs)) # contains definitions of each variable/column in our data
head(tibble(train_data)) # The training data for our model which will be split into test and train
head(tibble(test_data)) # The validation data for our model
head(tibble(Submissionsamp)) # The probability of each tour_id to be at a given category.

mean(is.na(train_data)) # if not zero then we have some missing values
mean(is.na(test_data)) # if not zero then we have some missing values

train_data_comp <- na.exclude(train_data) # exclude rows with any NA values
test_data_comp <- na.exclude(test_data) # exclude rows with any NA values

mean(is.na(train_data_comp)) # if not zero then we have some missing values
mean(is.na(test_data_comp)) # if not zero then we have some missing values

```
  The last datasets are complete with no missing values, we can now move on to visualizing our data.
  
```{r , message=FALSE, warning=FALSE}
#plot a graph to visualize the cost category distribution

#factor(train_data_comp$cost_category)
train_data_comp %>% summarise(cost_category) %>% ggplot(aes(cost_category)) + geom_histogram(stat = "count")

```

  If picked at random the probability of a tourist to be a in given cost category would follow this descending order:
  
  Normal Cost -> Higher Cost -> High Cost -> Low Cost -> Lower Cost -> Highest Cost
  
  To predict the cost of a single tourist correctly then we will have to investigate the variables and how they affect the cost category. Let us plot a correlation plot to get an initial picture.
  
```{r , warning=FALSE, message=FALSE}
library(corrplot)

# Make all the data numeric for correlation plots
factorized <- lapply(train_data_comp,as.factor)
corr_data <- lapply(factorized,as.numeric)
train_data_corr <- as.data.frame(corr_data)

# plot the graph
tdr <- cor(train_data_corr)
corrplot(tdr)
```

  The plot shows us that there is positive correlation between packages that tourists buy and that those packages have a negative correlation with the cost category.The higher the cost the more packages have been used. These variables will heavily affect our prediction models when tweaked.
  

## Machine Learning models

  The criteria in this project will be using the method of log loss.
  
```{r , warning=FALSE, message=FALSE}
library(caret)
library(RANN)
set.seed(28)
head(mtcars)

mtcars$vs <- as.factor(mtcars$vs)
train_ind <- createDataPartition(mtcars$vs, p = .8, 
                                  list = FALSE, times = 1)
mtcars_train <- mtcars[train_ind,]
mtcars_test <- mtcars[-train_ind,]

head(mtcars_train)
head(mtcars_test)

preProc <- preProcess(mtcars_train, method='knnImpute')
preProc

mtcars_train <- predict(preProc, newdata = mtcars_train)
anyNA(mtcars_train)

mtcars_glm_model <- train(form = vs ~ wt + disp + hp ,data = mtcars_train,
  trControl = trainControl(method = "cv", number = 5),
  method = "glm",family = "binomial"(link = "logit"))

mtcars_glm_model$results

```

  Now let us calculate the accuracy and the probabilities of the given model above.
  
```{r , message=FALSE, warning=FALSE}

calc_acc = function(actual, predicted) {
  mean(actual == predicted)
}

head(predict(mtcars_glm_model, newdata = mtcars_test))

calc_acc(actual = mtcars_test$vs,
         predicted = predict(mtcars_glm_model, newdata = mtcars_test))

head(predict(mtcars_glm_model, newdata=mtcars_test, type = "prob"))


```

```{r}
str(train_data)
```

  Now we will  test the model using our actual data for this project
  
### First Model   
  
```{r , warning=FALSE, message=FALSE}
library(VGAM) # method 'vglmAdjCat' is the one that worked
set.seed(26 )

train_data$cost_category <- as.factor(train_data$cost_category)
levels(train_data$cost_category) <- c("High_Cost","Higher_Cost", "Highest_Cost", "Low_Cost", "Lower_Cost", "Normal_Cost")

train_ind <- createDataPartition(train_data$cost_category, p = .8, 
                                  list = FALSE, times = 1)


train_set <- train_data[train_ind,]
test_set <- train_data[-train_ind,]

#preProc <- preProcess(as.data.frame(train_set), method = c("center", "scale", "YeoJohnson"))
#preProc

#train_set1 <- predict(preProc, newdata = train_set)

#anyNA(train_set1)

ctrl<-trainControl(method = "boot632", number=10, selectionFunction = "oneSE", classProbs = TRUE,  summaryFunction=mnLogLoss)
#grid<-expand.grid(parallel=FALSE, link= "loge") 


#nn_model <- nnet::multinom(cost_category ~ ., data= train_set)
mda_model <- train(form = cost_category ~ info_source + main_activity + package_transport_tz + package_transport_int + package_accomodation + package_food    + package_insurance + tour_arrangement ,data = train_set, trControl = ctrl,
  method = "vglmAdjCat", metric = "logLoss")

mda_model$results

```

### Second Model

```{r , warning=FALSE, message=FALSE}
library(caTools) 
set.seed(26 )

train_data$cost_category <- as.factor(train_data$cost_category)
levels(train_data$cost_category) <- c("High_Cost","Higher_Cost", "Highest_Cost", "Low_Cost", "Lower_Cost", "Normal_Cost")

train_ind <- createDataPartition(train_data$cost_category, p = .8, 
                                  list = FALSE, times = 1)


train_set <- train_data[train_ind,]
test_set <- train_data[-train_ind,]

preProc <- preProcess(as.data.frame(train_set), method = c("center", "scale", "YeoJohnson"))
#preProc

train_set1 <- predict(preProc, newdata = train_set)

#anyNA(train_set1)

ctrl<-trainControl(method = "boot632", number=10, selectionFunction = "oneSE", classProbs = TRUE,  summaryFunction=mnLogLoss)
grid<-expand.grid(nIter = 121) 


#nn_model <- nnet::multinom(cost_category ~ ., data= train_set)
mda_model <- train(form = cost_category ~ info_source + main_activity + package_transport_tz + package_transport_int + package_accomodation + package_food    + package_insurance + tour_arrangement ,data = train_set1, trControl = ctrl,
  method = "LogitBoost", metric = "logLoss", na.action = na.exclude, tuneGrid = grid)

mda_model$results

```
The above model has not performed well compared to the first model.

### Third Model

```{r , warning=FALSE, message=FALSE}
library(RWeka) 
set.seed(26 )

train_data$cost_category <- as.factor(train_data$cost_category)
levels(train_data$cost_category) <- c("High_Cost","Higher_Cost", "Highest_Cost", "Low_Cost", "Lower_Cost", "Normal_Cost")

train_ind <- createDataPartition(train_data$cost_category, p = .8, 
                                  list = FALSE, times = 1)


train_set <- train_data[train_ind,]
test_set <- train_data[-train_ind,]

preProc <- preProcess(as.data.frame(train_set), method = c("center", "scale", "YeoJohnson"))
#preProc

train_set1 <- predict(preProc, newdata = train_set)

#anyNA(train_set1)

ctrl<-trainControl(method = "boot632", number=10, selectionFunction = "oneSE", classProbs = TRUE,  summaryFunction=mnLogLoss)
grid<-expand.grid(iter = 20) 


#nn_model <- nnet::multinom(cost_category ~ ., data= train_set)
mda_model <- train(form = cost_category ~ info_source + main_activity + package_transport_tz + package_transport_int + package_accomodation + package_food    + package_insurance + tour_arrangement ,data = train_set1, trControl = ctrl,
  method = "LMT", metric = "logLoss", na.action = na.exclude, tuneGrid=grid)

mda_model$results

```
Worked better than the second model but not like the first model.

### Fourth Model

```{r , warning=FALSE, message=FALSE}
library(MASS) 
set.seed(26 )

train_data$cost_category <- as.factor(train_data$cost_category)
levels(train_data$cost_category) <- c("High_Cost","Higher_Cost", "Highest_Cost", "Low_Cost", "Lower_Cost", "Normal_Cost")

train_ind <- createDataPartition(train_data$cost_category, p = .8, 
                                  list = FALSE, times = 1)


train_set <- train_data[train_ind,]
test_set <- train_data[-train_ind,]

preProc <- preProcess(as.data.frame(train_set), method = c("center", "scale", "YeoJohnson"))
#preProc

train_set1 <- predict(preProc, newdata = train_set)

#anyNA(train_set1)

ctrl<-trainControl(method = "repeatedcv", number=60, selectionFunction = "oneSE", classProbs = TRUE,  summaryFunction=mnLogLoss)
#grid<-expand.grid(iter = 20) 


#nn_model <- nnet::multinom(cost_category ~ ., data= train_set)
mda_model <- train(form = cost_category ~ info_source + main_activity + package_transport_tz + package_transport_int + package_accomodation + package_food    + package_insurance + tour_arrangement ,data = train_set1, trControl = ctrl,
  method = "polr", metric = "logLoss", na.action = na.exclude)

mda_model$results

```
This model computes quickly but its results are the worst compared to all previous models.

### Fourth Model

```{r , warning=FALSE, message=FALSE}
library(ObliqueRF) 
set.seed(26 )

train_data$cost_category <- as.factor(train_data$cost_category)
levels(train_data$cost_category) <- c("High_Cost","Higher_Cost", "Highest_Cost", "Low_Cost", "Lower_Cost", "Normal_Cost")

train_ind <- createDataPartition(train_data$cost_category, p = .8, 
                                  list = FALSE, times = 1)


train_set <- train_data[train_ind,]
test_set <- train_data[-train_ind,]

preProc <- preProcess(as.data.frame(train_set), method = c("center", "scale", "YeoJohnson"))
#preProc

train_set1 <- predict(preProc, newdata = train_set)

#anyNA(train_set1)

ctrl<-trainControl(method = "cv", number=10, selectionFunction = "oneSE", classProbs = TRUE,  summaryFunction=mnLogLoss)
#grid<-expand.grid(iter = 20) 


#nn_model <- nnet::multinom(cost_category ~ ., data= train_set)
mda_model <- train(form = cost_category ~ info_source + main_activity + package_transport_tz + package_transport_int + package_accomodation + package_food    + package_insurance + tour_arrangement ,data = train_set1, trControl = ctrl,
  method = "ORFlog", metric = "logLoss", na.action = na.exclude)

mda_model$results

```



  Now let us calculate the accuracy and the probabilities of the given model above.
  
```{r , message=FALSE, warning=FALSE}

#head(predict(nn_model, newdata = test_set))

head(predict(mda_model, newdata=test_set, type = "prob"))


results_table <- predict(mda_model, newdata=test_set, type = "prob")

results_table <- results_table %>% rename(c("High Cost"=High_Cost,"Higher Cost"=Higher_Cost, "Highest Cost"=Highest_Cost, "Low Cost"=Low_Cost, "Lower Cost"=Lower_Cost, "Normal Cost"=Normal_Cost))

results_table <- results_table %>%
  add_column(Tour_ID = test_set$Tour_ID,
             .before = "High Cost") 

results_table

```
  We then create our submission file for the competition by getting results from our validation set.
  
```{r , message=FALSE, warning=FALSE}

head(predict(mda_model, newdata=test_data, type = "prob"))

final_table <- predict(mda_model, newdata=test_data, type = "prob")

final_table <- final_table %>% rename(c("High Cost"=High_Cost,"Higher Cost"=Higher_Cost, "Highest Cost"=Highest_Cost, "Low Cost"=Low_Cost, "Lower Cost"=Lower_Cost, "Normal Cost"=Normal_Cost))

final_table <- final_table %>%
  add_column(Tour_ID = test_data$Tour_ID,
             .before = "High Cost") 

final_table

write.csv(final_table,file = "final_table.csv", row.names = FALSE)


```
  Investigate the final file for missing values
  
```{r , warning=FALSE, message=FALSE}
final_table[final_table$Tour_ID=="tour_idnup62oa8",]

```

